\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=.7in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\Large}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}

\usepackage[usenames, dvipsnames]{color}
\definecolor{mygray}{gray}{0.6}
\definecolor{ao}{rgb}{0.0, 0.0, 1.0} 
\definecolor{blue(munsell)}{rgb}{0.0, 0.5, 0.69}

\usepackage[explicit]{titlesec}% http://ctan.org/pkg/titlesec
\def\Vhrulefill{\leavevmode\leaders\hrule height 0.0ex depth \dimexpr 0.3pt-0.0ex\hfill\kern0pt} %change both #.#ex to change height
\titleformat{\section}{\bfseries\Large}{}{0pt}{#1~\color{mygray}\Vhrulefill}
%\titleformat{\section}{\bfseries\Large}{}{0pt}{\noindent\Vhrulefill~#1~\Vhrulefill}

% Make lists without bullets
\renewenvironment{itemize}{
 \begin{list}{- }{
   \setlength{\leftmargin}{1.5em}
   \setlength{\itemsep}{0pt}
 }
}{
 \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  JESSICA L. BURNETT - Extended CV }}%- 0000-0002-0896-5099 }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={JESSICA L. BURNETT:  Extended CV (Curriculum Vitae)},
            pdfauthor={JESSICA L. BURNETT},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=maroon,
            citecolor=Blue,
            urlcolor=blue(munsell),
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf JESSICA L. BURNETT}

\vspace{2 mm}

\hrule

\vspace{2 mm}
%job title

%address

\moveleft.5\hoffset\centerline{ 
%github
\faGithub \hspace{1 mm} \href{http://github.com/trashbirdecology}{\color{black} trashbirdecology} \hspace{1 mm}   
%github
% \faTwitter \hspace{1 mm} \href{http://twitter.com/trashbirdecol}{\color{black} trashbirdecol} \hspace{1 mm}   
%phone
 \faMobile \hspace{1 mm}  +1 352 792 5425  \hspace{1 mm}  
%email
\faEnvelopeO \hspace{1 mm} \href{mailto:}{\color{black} \href{mailto:jburnett@usgs.gov}{\nolinkurl{jburnett@usgs.gov}}} \hspace{1 mm} 
%website
  | \emph{Updated:} \today}


\vspace{2 mm}

\hrule

\hypertarget{education}{%
\section{Education}\label{education}}

\textbf{Ph.D.} Natural Resource Sciences University of Nebrsaka-Lincoln
\hfill 2019\\
\textbf{M.Sc.} Wildlife Ecology \& Conservation, University of Florida
\hfill 2015\\
\textbf{B.Sc.} Wildlife Ecology \& Conservation University of Florida
\hfill 2013\\
\textbf{A.A.} General studies Valencia Community College \hfill 2010

\hypertarget{skills-highlight}{%
\section{Skills Highlight}\label{skills-highlight}}

\begin{itemize}
\tightlist
\item
  Applied statistics
\item
  Ecoinformatics
\item
  Ecological modeling
\item
  Reproducibility and open science 
\end{itemize}

\hypertarget{professional-experience}{%
\section{Professional Experience}\label{professional-experience}}

\textbf{Research Ecologist \& Mendenhall Postdoctoral Fellow}
\hfill September 2019 - present

U.S. Geological Survey, Lakewood, Colorado, USA

\begin{itemize}
\tightlist
\item
  Co-produced knowledge management systems for North American bird
  conservation
\item
  Co-investigator of Earth Science Information Partners research grant
\item
  Invited seminar presentation at University of Florida
\end{itemize}

\textbf{Graduate Research Assistant} \hfill August 2015 - August 2019

Nebraska Cooperative Fish \& Wildlife Research Unit\\
University of Nebraska-Lincoln, Nebraska, USA

\begin{itemize}
\tightlist
\item
  Advanced statistical methods for identifying abrupt change in
  ecological communities
\item
  Authored and maintained 5 scientific software packages:
\item
  Invited talk at Association for Women in Math Biology annual symposium
\item
  Published 8 peer-reviewed scientific articles and 1 invited book
  chapter
\item
  Co-creator of the University's Association for Women in Science and
  the Natural Resources Diversity Initiative 
\end{itemize}

\textbf{Young Scholar} \hfill May 2018 - September 2018

Applied Systems Analysis Research Group\\
International Institute for Applied Systems Analysis, Austria

\begin{itemize}
\tightlist
\item
  Conducted dissertation research with applied mathematician and systems
  scientists
\item
  Presented research in an international forum 
\end{itemize}

\textbf{Graduate Teaching Assistant} \hfill August 2013 - August 2015\\
Department of Wildlife Ecology \& Conservation\\
University of Florida, Florida, USA

\begin{itemize}
\tightlist
\item
  Published 2 peer-reviewed scientific articles
\item
  Invited lectures in data analysis and avian ecology
\end{itemize}

\textbf{Geospatial Analyst Intern} \hfill April 2012 - August 2012\\
Florida Fish and Wildlife Research Institute

\begin{itemize}
\tightlist
\item
  Data ground-truthing
\item
  Geospatial analysis of bird nest locations and success 
\end{itemize}

\textbf{Research Assistant} \hfill January 2011 - April 2012\\
Avian Ecology and Conservation Lab, University of Florida

\begin{itemize}
\tightlist
\item
  Managed bird banding database
\item
  Avian behavioral field research
\end{itemize}

\textbf{Crew Leader and Smithsonian Fellow} \hfill 2011 \& 2013\\
Neighborhood Nestwatch Program, Florida

\begin{itemize}
\tightlist
\item
  Trained and led team of banding technicians
\item
  Managed bird banding database
\item
  Recruited and trained participatory scientists
\item
  Created outreach materials
\end{itemize}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Erickson, R.A., \textbf{J.L. Burnett}, M.T. Wiltermuth, E.A. Bulliner,
  and L. Hsu (in review at \emph{Natural Resource Modeling}). Paths to
  computational fluency for natural resource managers and researchers.
\item
  \textbf{Burnett, J.L.}, L.S. Wszola, and G. Palomo-Munoz. 2019.
  bbsAssistant: An R package for downloading and handling data and
  information from the North American Breeding Bird Survey. Journal of
  Open Source Software, 4(44), 1768, DOI:
  \href{https://doi.org/10.21105/joss.01768}{10.21105/joss.01768}
\item
  Donovan, V.M., \textbf{J.L. Burnett}, C.H. Bielski, H.E. Birge, R.
  Bevans, D. Twidwell, and C.R. Allen. 2018. Social-ecological landscape
  patterns predict woody encroachment from native tree plantings in a
  temperate grassland \emph{Ecology and Evolution} 8(19): 9624-9632
  \url{DOI:10.1002/ece3.4340}
\item
  \textbf{Burnett, J.L.}, K.L. Pope, A. Wong, C.R. Allen, D.M. Haak,
  B.J. Stephen, and D.R. Uden. 2018. Thermal tolerance limits of the
  invasive Chinese mysterysnail \emph{Bellamya chinensis} and
  implications for management. \emph{American Malacological Bulletin}
  36(1): 140-144 \url{DOI:10.4003/006.036.0106}
\item
  Roberts, C.P., D. Twidwell, \textbf{J.L. Burnett}, V.M. Donovan, C.
  Wonkka, C.H. Bielski, A.S. Garmestani, D.G. Angeler, T. Eason, B.W.
  Allred, M.O. Jones, D.E. Naugle, S. Sundstrom, C.R. Allen . 2018.
  Early warnings for state transitions. \emph{Rangeland Ecology and
  Management} \url{DOI:10.1016/j.rama.2018.04.012}
\item
  La Sorte, F.A., C.A. Lepczyk, \textbf{J.L. Burnett}, A. Hurlbert, M.
  Tingley, and B. Zuckerberg. 2018. Opportunities and challenges for big
  data ornithology. \emph{The Condor} 120(2): 414-426
  \url{DOI:0.1650/CONDOR-17-206.1}
\item
  Chuang, W.C., A.S. Garmestani, T. Eason, T.L. Spanbauer, H.B.
  Fried-Peterson, C. Roberts, S. Sundstrom, \textbf{J.L. Burnett}, D. G.
  Angeler, B. Chaffin, L. Gunderson, D. Twidwell, C.R. Allen. 2018.
  Enhancing quantitative approaches for assessing ecological and
  community resilience. \emph{Journal of Environmental Management} 213:
  353-362 \url{DOI:10.1016/j.jenvman.2018.01.083}
\item
  \textbf{Burnett, J.L.}, C.R. Allen, C.P. Roberts, M.Bomberger Brown,
  and M.P. Moulton. 2017. Eurasian Tree Sparrow (\emph{Passer montanus})
  range expansion in North America. \emph{Biological Invasions} 19(1):
  5-9 \url{DOI:10.1007/s10530-016-1273-4}
\item
  \textbf{Burnett, J.L.} and K.E. Sieving. 2016. Songbird distress call
  as a detection enhancement method and application to Red-shouldered
  Hawks (\emph{Buteo lineatus}). \emph{Florida Field Naturalist}
  44(4):157-168
\item
  C.R. Allen, H.E. Birge, S.L. Bartlet-Hunt, R.A. Bevans, \textbf{J.L.
  Burnett}, B.A. Cosens, X. Cai, A.S. Garmestani, I. Linkov, E.A. Scott,
  M.D.~Solomon, and D.R. Uden. 2016. Avoiding decline: Fostering
  resilience and sustainability in midsize cities. \emph{Sustainability}
  8(9):844-868 \url{DOI:10.3390/su8090844}
\item
  \textbf{Burnett, J.L.} and M.P. Moulton. 2015. Recent trends in House
  Sparrow (\emph{Passer domesticus}) distribution and abundance in
  Gainesville, Alachua County, Florida. \emph{Florida Field Naturalist}
  43(4):167-172
\end{enumerate}

\hypertarget{book-chapters}{%
\section{Book Chapters}\label{book-chapters}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Burnett, J.L.} and C.R. Allen. 2020. Continental analysis of
  invasive Birds: North America \emph{in} Downs, C.T. and Hart, L.A.
  (eds) Invasive Birds: Global Trends and Impacts. CABI International,
  Wallingford, UK, pp.~278-294.
\end{enumerate}

\hypertarget{manuscripts-under-review-primary-author}{%
\section{Manuscripts Under Review (primary
author)}\label{manuscripts-under-review-primary-author}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Burnett, J.L.}, R. Wilcox, B. Stephen, D. Haak, D. Uden, C.R.
  Allen, and K. Pope. Shell strength does not limit predation of an
  invasive snail species (Bellamya chinensis) by native fish.
  \emph{under review at Malacological Bulletin}
\end{enumerate}

\hypertarget{notable-code-and-software}{%
\section{Notable Code and Software}\label{notable-code-and-software}}

\hypertarget{lifecycle-maturing-stable}{%
\subsubsection{Lifecycle: maturing,
stable}\label{lifecycle-maturing-stable}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Burnett, J.L.}, L.S. Wszola, and G. Palomo-Munoz. 2019.
  \href{https://github.com/TrashBirdEcology/bbsAssistant}{\texttt{bbsAssistant}}:
  An R package for downloading and handling data and information from
  the North American Breeding Bird Survey: U.S. Geological Survey
  software release. DOI:
  \href{https://doi.org/10.5066/P93W0EAW}{10.5066/P93W0EAW}.
\item
  Price, N.B., C. Chizinski, and \textbf{J.L. Burnett}.
  \texttt{radsets}. An R package for interactive, network-based
  visualizations of overlapping sets.
  \href{https://natbprice.github.io/radsets/}{Github:natbprice/radsets}
\item
  \textbf{Burnett, J.L.}, N.B. Price, and A.J. Tyre.
  \href{https://github.com/TrashBirdEcology/distancetravelled}{\texttt{distanceTravelled}}.
  An R package for calculating the distance traveled by a multispecies
  community along a time series.
\item
  Price, N.B. and \textbf{J.L. Burnett}. \texttt{tvdiff}. An R package
  for numerical differentiation of noisy, non-smooth data.
  \href{https://github.com/natbprice/tvdiff}{Github:natbprice/tvdiff}
\end{enumerate}

\hypertarget{lifecycle-dormant}{%
\subsubsection{Lifecycle: dormant}\label{lifecycle-dormant}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Burnett, J.L.}, N.B. Price.
  \href{https://github.com/TrashBirdEcology/regimedetectionmeasures}{\texttt{regimeDetectionMeasures}}.
  An R package for calculating univariate and multivariate regime
  detection methods using community time series.
\end{enumerate}

\hypertarget{lifecycle-experimental}{%
\subsubsection{Lifecycle: experimental}\label{lifecycle-experimental}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Burnett, J.L.}, K.R. Burgio, A. Fournier
  \href{https://github.com/TrashBirdEcology/USAvian/}{\texttt{USAvian}}:
  An interactive map for connecting and visualizing the bird
  conservation and management networks in the U.S.
\item
  \textbf{Burnett, J.L.}, X. Benito, and K. Braziunas.
  \href{http://github.com/regime-shifts/abruptdata}{\texttt{abruptdata}}.
  An R package and information repository for ecological datasets
  exhibiting abrupt change.
\end{enumerate}

\hypertarget{research-grants}{%
\section{Research Grants}\label{research-grants}}

\hypertarget{funded}{%
\subsection{Funded}\label{funded}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Wee, B., \textbf{J.L. Burnett}, S. Aulenbach, W. Teng, R.A. Modeling
  data and information needs for avian conservation using Neo4j. Earth
  Science Information Partners Lab \hfill \$3388
\item
  Pedersen, E., \textbf{J.L. Burnett}, G. Simpson, C. Bahlai.
  \textbf{2020}. Creating a unified approach to evaluate regime shift
  detection methods. Canadian Institution for Ecology and Evolution
  (CIEE) \hfill \textbf{\$12,400 CAD}
\item
  \textbf{J.L. Burnett}. \textbf{2019-21}. Mendenhall Postdoctoral
  Research, Core Science Systems Science Analytics and Synthesis, U.S.
  Geological Survey. \hfill \textbf{\textasciitilde{}\$222,000}
\item
  International Institute for Applied Systems Analysis (IIASA)
  \href{https://iiasa.ac.at/web/home/education/yssp/Young_Scientists_Summer_Program.html}{Young
  Scholar Summer Program}. \textbf{2018}. Funding sources: National
  Academy of Sciences and University of Nebraska-Lincoln.
  \hfill \textbf{\textasciitilde{}\$12,500}
\end{enumerate}

\hypertarget{not-funded}{%
\subsection{Not Funded}\label{not-funded}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Pedersen, E., \textbf{J.L. Burnett}, G. Simpson, C. Bahlai. Creating a
  unified approach to evaluate regime shift detection methods. Powell
  Center Synthesis Working Group, U.S. Geological Survey \hfill 2020 
\item
  Informing the design and deployment of a conservation tool, USAvian:
  learning through co-production, synthesizing lessons learned.
  Community for Data Integration, U.S. Geological Survey \hfill 2020 
\item
  Benito, X., C. Bahlai, \textbf{J.L., Burnett}, E. Pedersen, and G.
  Simpson. SESYNC working group proposal. \hfill  2019\\
\item
  \textbf{Burnett, J.L.}. Population Biology Program of Excellence (PoE)
  Postdoctoral Fellowship, University of Nebraska-Lincoln \hfill 2018\\
\item
  \textbf{Burnett, J.L.}, C.R. Allen, G. Sugihara, and H. Ye. Scale
  mismatches in ecological research and management: consequences and
  solutions through data management. Powell Center Synthesis Working
  Group, U.S. Geological Survey \hfill 2018\\
\item
  \textbf{Burnett, J.L.} Mozilla Fellowship for Science \hfill 2016\\
\item
  \textbf{Burnett, J.L.} NSF Graduate Research Fellowship \hfill 2013
\end{enumerate}

\hypertarget{fellowships-honors-awards}{%
\section{Fellowships, Honors \&
Awards}\label{fellowships-honors-awards}}

\hypertarget{section}{%
\subsubsection{2020}\label{section}}

\begin{itemize}
\tightlist
\item
  Invited workshop participant, Future of Synthesis in Ecology, NCEAS
\end{itemize}

\hypertarget{section-1}{%
\subsubsection{2019}\label{section-1}}

\begin{itemize}
\tightlist
\item
  School of Natural Resources, University of Nebraska-Lincoln
  \hfill \textbf{\$750}
\item
  University of Nebraska Graduate Travel Fund \hfill \textbf{\$750}
\item
  Association for Women in Mathematical Biology \hfill \textbf{\$650}
\item
  School of Natural Resources, University of Nebraska-Lincoln
  \hfill \textbf{\$1050}
\end{itemize}

\hypertarget{section-2}{%
\subsubsection{2018}\label{section-2}}

\begin{itemize}
\tightlist
\item
  \href{http://snr.unl.edu/aboutus/what/awardscomplete.asp}{Meritorious
  Graduate Student} award, School of Natural Resources, UNL
  \hfill \textbf{\$500}
\item
  National Academy of Sciences research award \hfill \textbf{\$5,500}
\item
  Invited workshop participant,
  \href{http://www.nimbios.org/education/WS_wwmb}{Research Collaboration
  Workshop for Women in Mathematical Biology, NIMBIOS}
  \hfill \textbf{\$900}
\item
  National Science Foundation \& NimBios \hfill \textbf{\$550}
\item
  Nelson Memorial Fellowship, University of Nebraska-Lincoln \emph{(3x
  recipient, 2016, 17, 18)} \hfill  \textbf{totaling \$3,217}
\item
  Center for Great Plains Studies travel award, University of
  Nebraska-Lincoln \emph{(4x recipient; 2015, 2016, 2017, 2018)}
  \hfill \textbf{totaling \$3,000}
\end{itemize}

\hypertarget{section-3}{%
\subsubsection{2017}\label{section-3}}

\begin{itemize}
\tightlist
\item
  Kellogg Biological Station, Michigan State University
  \hfill \textbf{\$500}
\item
  Big Ten Academic Alliance Traveling Scholar
\end{itemize}

\hypertarget{section-4}{%
\subsubsection{2016}\label{section-4}}

\begin{itemize}
\tightlist
\item
  2nd place, School of Natural Resources Elevator Speech Competition
  \hfill \textbf{\$300}
\item
  American Ornithologists' Union travel award \hfill \textbf{\$250}
\item
  Fling Fellow, University of Nebraska-Lincoln \hfill \textbf{\$20,000}
\item
  Othmer Fellow, University of Nebraska-Lincoln \hfill \textbf{\$24,000}
\item
  AAAS/Science Program for Excellence in Science Award
\item
  Graduate Fellow, Center for Great Plains Studies, University of
  Nebraska
\end{itemize}

\hypertarget{section-5}{%
\subsubsection{2015}\label{section-5}}

\begin{itemize}
\tightlist
\item
  Resilience Alliance Young Scholar, The Resilience Alliance (2015-2017)
  \hfill 2015 - 17
\item
  NSF Diversity Travel Award, Southeastern Ecology and Evolution
  Conference \hfill \textbf{\$650}
\item
  Graduate Student Council, University of Florida \hfill \textbf{\$350}
\item
  Office of Research, University of Florida \hfill \textbf{\$350}
\end{itemize}

\hypertarget{section-6}{%
\subsubsection{2014}\label{section-6}}

\begin{itemize}
\tightlist
\item
  Travel Award, Department of Wildlife Ecology \& Conservation,
  University of Florida \emph{(2x recipient)} \hfill \textbf{\$500}
\end{itemize}

\hypertarget{section-7}{%
\subsubsection{2013}\label{section-7}}

\begin{itemize}
\tightlist
\item
  Travel Award, Office of the Dean, Institute of Food and Agricultural
  Sciences, University of Florida \hfill \textbf{\$750}
\item
  American Ornithologists' Union Undergraduate Student Membership Award
  \hfill 
\item
  IFAS Extension Internship for Undergraduate Research, University of
  Florida \hfill  \textbf{\$2,200}
\item
  Ordway-Swisher Biological Station Undergraduate Research Grant,
  University of Florida \hfill  \textbf{\$550}
\end{itemize}

\hypertarget{organized-sessions-symposia}{%
\section{Organized Sessions \&
Symposia}\label{organized-sessions-symposia}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Using the integrated modelling framework to bridge science and
  decision making: advances, applications, and opportunities.
  Co-organizer with J.A. Royle. Ecological Society of America conference
  \hfill 2020
\item
  Bridging the gap between science and decision-making through the rapid
  prototyping of decision support tools. Co-organizer with D. Valle and
  L.S. Wszola. Ecological Society of America conference \hfill 2020
\item
  Opportunities and Challenges in Big Data Ornithology. Co-organizer
  with F.A. LaSorte and C.A. Lepczyk. North American Ornithological
  Conference V, Washington, D.C. \hfill 2016
\end{enumerate}

\hypertarget{presentations-primary-author}{%
\section{Presentations (primary
author)}\label{presentations-primary-author}}

\hypertarget{invited}{%
\subsection{Invited}\label{invited}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Integrating data and information to enhance the digital efficeincy of
  wildlife conservation and management. North American Ornithological
  Conference \hfill 2020
\item
  Regime Detection Measures for the Pratical Ecologist, Department of
  Wildlife Ecology \& Conservation, University of Florida \hfill 2019
\item
  Detecting abrupt change in bird community time series using distance
  travelled. \emph{Association for Women in Math Biology Symposium},
  Special session ``Current Challenges in Mathematical Biology'',
  Houston, TX \hfill 2019
\item
  Decline of the Once-Ubiquitous House Sparrow in North America.
  \emph{Nebraska Invasive Species Council}, Lincoln, NE \hfill 2015
\end{enumerate}

\hypertarget{contributed}{%
\subsection{Contributed}\label{contributed}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Burnett, J.L.}, N.B. Price, and A.J. Tyre. A novel method for
  tracking ecosystem trajectory and abrupt change in space-time:
  distance traveled. \emph{International Association for Landscape
  Ecology}, Oral presentation. Fort Collins, CO, 2019
\item
  \textbf{Burnett, J.L.}, R. Crystal-Ornelas, D. Fogarty, K. Hogan, C.R.
  Allen, M. Bomberger Brown, D. Twidwell, and C.A. Lepczyk. Impacts of
  non-native birds on native wildlife in urban ecosystems: where is the
  evidence? \emph{Natural Areas Conference}, Oral presentation. Indiana,
  2018
\item
  \textbf{Burnett, J.L.}. Advances in ecological regime shift detection,
  \emph{International Institute for Applied Systems Analysis}, Oral
  presentation. Laxenburg, Austria, 2018
\item
  \textbf{Burnett, J.L.}, N.B. Price, A.J. Tyre, T.J. Hefley, C.R.
  Allen, T. A. Eason, D.G. Angeler,and D. Twidwell. Community velocity
  as a regime shift detection method. \emph{Great Plains Grassland
  Summit}, Poster presentation. Denver, Colorado, 2018
\item
  \textbf{Burnett, J.L.}, L. Wszola, N. Mirochnitchenko, E. Stuber, M.
  Bomberger Brown, C.R. Allen, D. Twidwell, and J.P. Carroll. Gray
  partridge distribution in North America: Changing landscapes and
  environment for an introduced species. Perdix XIV and IUGB, Oral
  presentation by JPC, Montpellier, France, 2017
\item
  \textbf{Burnett, J.L.}, N.B. Price, A.J. Tyre, T.J. Hefley, C.R.
  Allen, T. A. Eason, D.G. Angeler,and D. Twidwell. System trajectory
  and Fisher information as early-warning indicators of ecological
  regime shifts. \emph{Resilience 2017: Resilience Frontiers for Global
  Sustainability}, Poster presentation. Stockholm, Sweden, 2017
\item
  \textbf{Burnett, J.L.}, N.B. Price, A.J. Tyre, T.J. Hefley, C.R.
  Allen, T. A. Eason, D.G. Angeler,and D. Twidwell. System trajectory
  and Fisher information as early-warning indicators of ecological
  regime shifts. \emph{Ecological Society of America}, Poster
  presentation. Portland, OR, 2017
\item
  \textbf{Burnett, J.L.}, Roberts, C.P., Allen, C.R., Angeler, D.G.,
  Twidwell, D., and Tyre, A.J. Ecological Regime Shifts in the Central
  Great Plains. \emph{Great Plains Symposium}, Oral presentation.
  Nebraska Innovation Campus, Lincoln, NE, 2017
\item
  \textbf{Burnett, J.L.}, Roberts, C.P., Allen, C.R., Angeler, D.G.,
  Twidwell, D., and Tyre, A.J. Using Big Data to Detect Regime Shifts in
  Space and Time. \emph{North American Ornithological Conference VI},
  Poster presentation. Smithsonian Migratory Bird Institute, Washington,
  D.C., 2016
\item
  \textbf{Burnett, J.L.}, Moulton, M. P., Sieving, K.E., Avery, M., and
  Robinson, S.K. Are House Sparrow declines a byproduct of urban
  greening? Southeastern Ecology and Evolution Conference, Oral
  presentation. University of Georgia, Athens, GA, 2015
\item
  \textbf{Burnett, J.L.}, Moulton, M. P., Sieving, K.E., Avery, M.L.,
  and Robinson, S.K. Are House Sparrow declines a byproduct of urban
  greening? \emph{American Ornithologists' Union and Cooper
  Ornithological Society Annual Meeting}, Poster presentation. Norman,
  OK, 2015
\item
  \textbf{Burnett, J.L.}, Moulton, M.P., and Sieving, K.E. House
  sparrow: the decline of a once ubiquitous, invasive species.
  \emph{Florida Chapter of The Wildlife Society Annual Conference},
  Poster presentation. Safety Harbor, FL, 2014.
\item
  \textbf{Burnett, J.L.}, Moulton, M. P., Sieving, K.E., Avery, M.L.,
  and Robinson, S.K. House Sparrow decline and distribution in North
  Central Florida. \emph{Florida Cooperative Fish and Wildlife Research
  Unit annual cooperators meeting}, Poster presentation. Gainesville,
  FL, 2014
\item
  \textbf{Burnett, J.L.} and Sieving, K.E. Detecting birds of prey using
  tufted titmouse distress calls. \emph{USGS Florida Cooperative Fish
  and Wildlife Research Unit Committee Meeting}, Poster presentation.
  Gainesville, FL, 2013
\item
  \textbf{Burnett, J.L.} and Sieving, K.E. Do actual and perceived risks
  of small forest birds align? \emph{Florida Ornithological Society
  Conference, Oral presentation}, St.~Petersburg, FL, 2013
\item
  \textbf{Burnett, J.L.} and Sieving, K.E. Perceived predation risks of
  small forest birds. \emph{Association of Field Ornithologists Annual
  Conference}, Poster presentation. Venus, FL, 2013
\end{enumerate}

\hypertarget{scientific-outreach}{%
\section{Scientific Outreach}\label{scientific-outreach}}

\hypertarget{community-involvement}{%
\subsection{Community Involvement}\label{community-involvement}}

\begin{itemize}
\tightlist
\item
  Letters to a Pre-scientist, United States \hfill 2019-present
\item
  Skype a Scientist, United States \hfill 2017-present
\item
  Co-PI, Community grant to develop on-site nature trail and viewing
  opportunities at the Reichert House, Gainesville, FL \hfill 2014-15
\item
  Hands-on captive herpetological opportunities for studnets of the
  Reichert House, Gainesville, FL \hfill 2014-15
\item
  Birdwatching and live banding demonstrations for K-12 students, A
  Girls' Place, Gainesville, FL \hfill 2013-15
\item
  Science, mathematics and reading tutor for middle and high school
  students, Friends of the Micanopy Library, FL \hfill 2011-13
\item
  Learning assistant and tutor for geometry and pre-calculus students,
  Valencia Community College, Oralndo, FL \hfill 2008-10
\end{itemize}

\hypertarget{blogs}{%
\subsection{Blogs}\label{blogs}}

\begin{itemize}
\tightlist
\item
  \href{https://envirobites.org/2017/10/17/connecting-to-nature-and-understanding-ecosystem-services-the-urban-perspective/}{Connecting
  to nature and understanding ecosystem services: urban perspective},
  Envirobites
\item
  \href{http://resilience2017.org/blog/big-data-big-problems/}{Big data,
  big problems}, Resilience Alliance
\item
  \href{http://resilience2017.org/blog/panarchy-in-the-anthropocene/}{Panarchy
  in the Anthropocene}, Resilience Alliance -
  \href{http://resilience2017.org/blog/regime-shifts-traps-and-how-to-deal-with-them/}{Regime
  shifts, traps and how to deal with them}, Resilience Alliance
\item
  \href{http://resilience2017.org/blog/connecting-to-nature-and-understanding-ecosystem-services-the-urban-perspective/}{Connecting
  to nature and understanding ecosystem services: the urban
  perspective}, Resilience Alliance
\item
  \href{http://resilience2017.org/blog/leadership-resilience-and-your-workplace/}{Leadership
  resilience and your workplace}, Resilience Alliance
\end{itemize}

\hypertarget{radio}{%
\subsection{Radio}\label{radio}}

\begin{itemize}
\tightlist
\item
  \href{http://www.urbanwildlifecast.com/?p=139}{House Sparrow declines
  in North American, Urban Wildlife Podcast}
\end{itemize}

\hypertarget{service}{%
\section{Service}\label{service}}

\hypertarget{department-of-interior}{%
\subsection{Department of Interior}\label{department-of-interior}}

\begin{itemize}
\tightlist
\item
  Advisory committee member for the Fish and Wildlife Service Avian
  Knowledge Network (AKN)
\item
  Member, Communications and Marketing Committee for the North American
  Breeding Bird Survey 2020 Action Plan
\end{itemize}

\hypertarget{peer-review-activity}{%
\subsection{Peer Review Activity}\label{peer-review-activity}}

\begin{itemize}
\tightlist
\item
  Department of Interior: {[}Abstracts (2), Research Articles (1),
  Software/code (1), Reports (1){]}
\item
  Code and software: \emph{Journal of Open Source Software} (3),
  \emph{ReScience} (1)
\item
  Scientific manuscripts: \emph{Bioinvasions Records} (1),
  \emph{Conservation Biology} (1), \emph{Ecological Informatics} (4)
  \emph{Ecological Modelling} (4), \emph{Journal of Molluscan Studies}
  (2), \emph{Landscape and Urban Planning} (1 pending), \emph{PLOS One}
  (1), \emph{Wilson Journal of Ornithology} (3)
\end{itemize}

\hypertarget{university-of-nebraska-lincoln}{%
\subsection{University of
Nebraska-Lincoln}\label{university-of-nebraska-lincoln}}

\begin{itemize}
\tightlist
\item
  Co-founder, Natural Resources Diversity Initiative committee, School
  of Natural Resources \hfill 2017
\item
  Co-founder,
  \href{http://news.unl.edu/newsrooms/today/article/university-is-institutional-partner-with-association-for-women-in-science/}{Institutional
  membership to the Association for Women in Science} \hfill 2016
\item
  \href{http://snr.unl.edu/employeeinfo/people/committee/facultyadvisory.asp}{Faculty
  Advisory Committee}, School of Natural Resources \hfill 2016-18
\item
  Digital Team, School of Natural Resources \hfill 2016
\item
  Organizer, Association for Women in Science
  \href{http://snr.unl.edu/registration/AWISMentor/MentorMenteeRegistrationAttendanceCap.aspx?utm_source=Google\&utm_medium=email\&utm_term=\&utm_content=\&utm_campaign=AWIS+Workshop}{Mentor
  Workshop} \hfill 2016
\item
  \href{http://unlcms.unl.edu/snr/gsa/snr-gsa-seminar-coordinators}{Seminar}
  Coordinator, School of Natural Resources \hfill 2016
\item
  Department Representative, UNL Graduate Student Association
  \hfill 2015 - 16
\end{itemize}

\hypertarget{reports}{%
\section{Reports}\label{reports}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Burnett, J.L.}, Roberts, C.P., Allen, C.R., Angeler, D.G.,
  Twidwell, D. 2017. White Paper: Regime Shift Detection Using Fisher
  Information. Strategic Environmental Research and Development Program
  (SERDP RC 25-10), Department of Defense.\\
\item
  Allen, C.R., Angeler, D.G., Twidwell, D., \textbf{Burnett, J.L.},
  Roberts, C.P. 2017. Interim Report (RC 25-10): Global Change,
  Vulnerability, and Resilience: Management Options for an Uncertain
  Future. Strategic Environmental Research and Development Program
  (SERDP), Department of Defense.\\
\item
  Twidwell D., Bielski, C.H., \textbf{Burnett, J.L.}, Donovan, V.M.,
  Wonkka, C.L. 2017. Review of LANDFIRE Biophysical Settings Models
  (BpS) in the Great Plains. LANDFIRE Project.
\end{enumerate}

\end{document}
