---
name: Jessica Burnett, Ph.D.
address: 5067 6th Place NE, Washington, D.C. 20017
phone: (720) 730-0974
# email: jessica.burnett@nasa.gov
email: jessicaleighburnett@gmail.com
# website: https://github.com/trashbirdecology
geometry: left=1in,right=1in,top=1in,bottom=1in
bibliography: data/publications.bib
csl: csl/science.csl
knit: (function(input, ...) {
    c(
    rmarkdown::render(
      input,
      output_format = "pdf_document",
      output_file = "burnett_2pg_step",
      envir = globalenv()
    ),
      rmarkdown::render(
      input,
      output_format = "github_document",
      output_file = "README",
      envir = globalenv()
    ),
    rmarkdown::render(
      input,
      output_format = "word_document",
      output_file = "burnett_fedresume",
      envir = globalenv()
    )
    )
  })
output:
  output:
  pdf_document:
    extra_dependencies:
      fontawesome: null
      carlito: sfdefault
      fancyhdr: null
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(fontawesome)
library(rmarkdown)
```

\vspace*{-0.75in}
\thispagestyle{empty}
\centerline{\huge \bf `r metadata$name`}
\vspace{5pt}
\centerline{
\faicon{map-marker} `r metadata$address` \hspace{2 pt}
\faicon{phone} \href{tel:`r gsub("[[:space:]]", "", metadata$phone)`}{`r metadata$phone`} \hspace{2 pt}
\faicon{envelope} \href{mailto:`r metadata$email`}{`r metadata$email`} \hspace{2 pt}
}
\vspace{5pt}
\hrule

\pagestyle{fancy}
\fancyhead[L]{\textcolor[gray]{0.4}{Resume: `r metadata$name`}}
\fancyfoot[L]{\textcolor[gray]{0.4}{Document compiled on `r Sys.Date()` (\href{https://www.github.com/trashbirdecology/cv}{github.com/trashbirdecology/cv})}}
\pagenumbering{gobble}

```{r, results='asis', eval = knitr::is_html_output()}
cat("# ", metadata$name, "\n")
fa("map-marker")
cat("&nbsp;&nbsp;&nbsp;", metadata$address, "&nbsp;&nbsp;&nbsp;")
fa("phone")
cat("&nbsp;&nbsp;&nbsp;", metadata$phone, "&nbsp;&nbsp;&nbsp;")
fa("envelope")
cat("&nbsp;&nbsp;&nbsp;", metadata$email, "&nbsp;&nbsp;&nbsp;")
fa("home")
# cat('&nbsp;&nbsp;&nbsp;<a href="https://',
#   metadata$website,
#   '">',
#   metadata$website,
#   "</a>",
#   "&nbsp;&nbsp;&nbsp;",
#   sep = ""
# )
cat("<hr/>")
```

## Key Skills
- Well-published Ph.D. Earth science researcher with 16 publications in top Earth science journals, 1 book chapter, 3 software programs, and numerous government white papers and reports.
- Experience developing and applying cutting-edge Bayesian and frequentist statistical methods to support ecosystems management and understanding. 
- Over 7 years experience designing and implementing multi-year programs to answer important scientific questions, generate actionable intelligence for end user organizations, create cross-program synergies, and advance government agency missions.
-	Passionate relationship builder whose efforts have resulting in NASA being a recognized and sought-after partner for achieving wildlife management and conservation goals in North America.
- Over a decade of experience in integrating and managing concurrent research projects with an emphasis on Earth and life sciences including wildlife conservation, applied geospatial science, scientific programming, and statistical modeling.
- Judicious communicator with strong interpersonal and presentation skills who has proven experience in presenting to audiences of up 500 people in person and via audio and video conferencing platforms with presentations to lay audiences, scientific communities, and decision makers alike.
- Experience in developing, evaluating, marketing, and measuring progress of competitive funding solicitations.
  <!-- Program/Project Management -->
  <!-- Geospatial Science and Technologies -->
  <!-- Strategic Thinking -->
  <!-- Earth Science Applications Research -->
  <!-- Partnering -->
  <!-- Financial Management -->
  <!-- Technical Competence -->
  
## Education
**Ph.D. in Natural Resource Sciences**, *University of Nebraska-Lincoln*, Lincoln, Nebraska | 2019 \
**M.S. in Wildlife Ecology & Conservation**, *University of Florida*, Gainesville, Florida | 2015 \
**B.S. in Wildlife Ecology & Conservation**, *University of Florida*, Gainesville, Florida | 2013 \
**A.A. in General Studies**,*Valencia Community College*, Orlando, Florida | 2010

## Professional Experience <!-- Skills, evidence, why it matters -->
**National Aeronautics and Space Administration (NASA) **, Washington, D.C. US \
*Program Coordinator, Ecological Conservation, Earth Science Division* | August 2022 - Present

- Represent NASA in high-level federal governmental and interorganizational efforts.
- Cultivate collaborative partnerships with federal, state, and non-governmental conservation organizations and landowners. 
- Serve as a technical expert on ecology and conservation issues for data calls from agencies like the White House Office of Science and Technology Policy (OSTP).
- Champion and empower students from underrepresented backgrounds, directing and supervising projects pivotal to program development, evaluation, and expansive outreach initiatives.

**U.S. Geological Survey (USGS), Biogeographic Sciences Branch**, Denver, Colorado, US \
*Research Ecologist and Data Scientist (GS-12-3)* | August 2019 - August 2022 

- Develop cutting-edge statistical (Bayesian) methods for estimating bird population parameters. 
- Key player in establishing cross-organizational relationships.
- Published 3 peer-reviewed papers in top Earth Science journals.
- Participated in several initiatives focused on diversifying the scientific professional and academic communities.

**University of Nebraska-Lincoln (UNL)**, Lincoln, Nebraska, US \
*Statistical and Applied Ecology Graduate Research Assistant* | August 2015 - July 

- Spearheaded the development of UNL's Association for Women in Science and Natural Resources Diversity Initiative.
- Published peer reviewed articles in top natural resources and computational journals.
- Managed multiple, concurrent research projects with international and domestic collaborators, leading outreach efforts to improve applications of products for natural resource management at U.S. military bases.

**International Institute for Applied Systems Analysis (IIASA)**, Laxenburg, Austria \
*Visiting Researcher for Applied Systems Analysis* | April 2018 - August 2018

- First-time recipient (of over 500 international applicants) of the renowned Young Scholar Summer Program fellowship, with financial support competitively awarded by the U.S. National Academy of Sciences.
- Designed and led collaborative research with applied mathematicians and Earth scientists, resulting in multiple international presentations, a peer-reviewed journal article, and software releases.

**University of Florida (UF)**, Gainesville, Florida, US \
*Invasion and Avian Ecology Graduate Research Assistant* | August 2013 - August 2015 
- Designed and conducted research resulting in 3 publications and becoming a top expert on urban bird populations.
- Taught and mentored undergraduate students, including developing workshops and lectures on the topics of scientific programming, invasive species, and geospatial modeling.

## Notable Awards & Achievements
- AAAS Science & Technology Policy Fellowship
- U.S. Geological Survey Mendenhall Postdoctoral Research Fellowship

## Publications
Full List Available On Google Scholar: https://scholar.google.com/citations?user=L0t-rQoAAAAJ&hl=en&oi=ao

## Presentations
Over 30 oral presentations a scientific conferences, interagency meetings, and to international audiences in the last 10 years.

## Select Conferences, Workshops & Symposia Coordination
1. Applied Earth Observations Innovation Partnership annual workshop (~200 attendees). *Workshop organizer*, Ann Arbor, 2024
1. NASA Biodiversity & Ecological Conservation annual science and applications team meeting (~250 attendees, ~75 sessions). *Conference co-organizer*, Washington, D.C., 2024
1. NASA Ecological Conservation annual retreat. *Workshop co-organizer and moderator*, Kennedy Space Center, 2024.
1. NASA Earth Science Data and Compute workshop. *Workshop organizer and moderator* (~75 attendees), College Park, MD, 2023
1. NASA Carbon Cycle and Ecosystems Joint Science Workshop. *Conference co-organizer and moderator* (~500 attendees), College Park, MD, 2023
1. Applied Earth Observations Innovation Partnership annual workshop. *Workshop co-organizer* (~200 attendees), Salt Lake City, UT, 2023
1. NASA Ecological Conservation annual retreat. *Workshop co-organizer and moderator*, Tampa, FL, 2023.

<!-- # Essay
## Current Fellowship at NASA Headquarters
I am currently hosted at NASA Headquarters in the Earth Science Division, focusing on outreach, engagement, and partnerships within the Ecological Conservation program, which funds global projects aimed at biodiversity conservation. My primary goal during this fellowship has been to make NASA's resources more accessible to fisheries and wildlife scientists, managers, and decision-makers. Through my efforts, I have successfully facilitated connections between NASA and these stakeholders, enhancing the impact of our conservation initiatives. 

## Interest in Science Diplomacy 
I am particularly interested in learning more about science diplomacy to expand my skillset and better engage in international forums. During my fellowship, I have developed strong relationships with conservation leaders and organizations in the U.S., including federal, state, and tribal entities. However, my limited experience in international science diplomacy restricts my effectiveness in global contexts. Understanding science diplomacy will enable me to participate more actively in NASA's international activities, such as IPBES, CoP, and UN subcommittees related to Earth and biodiversity science, thereby enhancing my contributions to these important initiatives.  

 ## Interest in International Collaboration

My interest in international collaboration, especially with science-policy fellows from Latin America and the Caribbean (LAC), stems from the recognition of the importance of these regions in global biodiversity. Although my work has predominantly focused on U.S. organizations, NASA funds several projects in the Caribbean and South America. Developing diplomatic and collegial relationships with organizations influencing on-the-ground decision-making and policy in these regions is crucial. By learning to better build and maintain these relationships, I aim to foster effective collaborations that can address shared ecological challenges and promote sustainable conservation efforts across borders. -->  

