---
name: Jessica Burnett, Ph.D.
address: Washington, D.C.
phone: +1 720 730 0974
email: jessica.burnett@nasa.gov
# website: https://github.com/trashbirdecology
geometry: left=1in,right=1in,top=1in,bottom=1in
bibliography: data/publications.bib
nocite: |
  @test
knit: (function(input, ...) {
    c(rmarkdown::render(
      input,
      output_format = "github_document",
      output_file = "README",
      envir = globalenv()
    ),
    rmarkdown::render(
      input,
      output_format = "pdf_document",
      output_file = "burnett_resume",
      envir = globalenv()
    ))
  })
output:
  pdf_document:
    extra_dependencies:
      fontawesome: null
      carlito: sfdefault
      fancyhdr: null
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(fontawesome)
library(rmarkdown)
```

\vspace*{-0.75in}
\thispagestyle{empty}
\centerline{\huge \bf `r metadata$name`}
\vspace{5pt}
\centerline{
\faicon{map-marker} `r metadata$address` \hspace{2 pt}
\faicon{phone} \href{tel:`r gsub("[[:space:]]", "", metadata$phone)`}{`r metadata$phone`} \hspace{2 pt}
\faicon{envelope} \href{mailto:`r metadata$email`}{`r metadata$email`} \hspace{2 pt}
\faicon{home} \href{https://`r metadata$website`}{`r metadata$website`}
}
\vspace{5pt}
\hrule

\pagestyle{fancy}
\fancyhead[L]{\textcolor[gray]{0.4}{Resume: `r metadata$name`}}
\fancyfoot[L]{\textcolor[gray]{0.4}{Document compiled on `r Sys.Date()` (\href{https://www.github.com/trashbirdecology/cv}{github.com/trashbirdecology/cv})}}
\pagenumbering{gobble}

```{r, results='asis', eval = knitr::is_html_output()}
cat("# ", metadata$name, "\n")
fa("map-marker")
cat("&nbsp;&nbsp;&nbsp;", metadata$address, "&nbsp;&nbsp;&nbsp;")
fa("phone")
cat("&nbsp;&nbsp;&nbsp;", metadata$phone, "&nbsp;&nbsp;&nbsp;")
fa("envelope")
cat("&nbsp;&nbsp;&nbsp;", metadata$email, "&nbsp;&nbsp;&nbsp;")
fa("home")
cat('&nbsp;&nbsp;&nbsp;<a href="https://',
  metadata$website,
  '">',
  metadata$website,
  "</a>",
  "&nbsp;&nbsp;&nbsp;",
  sep = ""
)
cat("<hr/>")
```

## Education

**Doctorate | Natural Resources Science** \
*University of Nebraska-Lincoln*, Lincoln, Nebraska, US | 2019 \

**Master of Science | Wildlife Ecology & Conservation** \
*University of Florida*, Gainesville, Florida, US | 2015

**Bachelor of Science | Wildlife Ecology & Conservation** \
*University of Florida*, Gainesville, Florida, US  | 2013

**Associate of Arts | General Studies** \
*Valencia Community College*, Orlando, Florida, US  | 2010


## Key Skills
- Demonstrated experience in strategic relationships with federal and state partners
- Sought-after partner of U.S. state and federal natural resource management agencies and non-governmental conservation organizations  
- Strategic thinker
- Proven steward of federal ?
<!-- Program/Project Management -->
<!-- Geospatial Science and Technologies -->
<!-- Strategic Thinking -->
<!-- Earth Science Applications Research -->
<!-- Partnering -->
<!-- Financial Management -->
<!-- Technical Competence -->


## Professional Experience
<!-- SKills, evidence, why it matters -->
**National Aeronautics and Space Administration**, Washington, D.C., US \
*Associate Program Manager* | August 2022 - Present \

- One of two NASA fellows (of over XXXX applicants) AAAS Science & Technology Policy Fellowship
- Established key interagency relationships with key U.S. federal, state, and non-governmental conservation organization resulting in increased awareness of NASA Earth Science Division 
- Designed and conducted targeted outreach to U.S. federal, state, and non-governmental organizations resulting in a two-fold increase in number of proposal submissions
- Initiated and led efforts to develop strategic plan for maximizing program investments 
- Represented NASA on interagency science and technology committees to enable application of NASA data and investments by federal partners
- Mentored undergraduate and high school students from traditionally underrepresented backgrounds to conduct projects resulting in actionable intelligence for program evaluation and outreach to 
- Served as technical expert for conservation issues on data and information calls from the White House Office of Science and Technology Policy
- Provided technical expertise on NASA Open Science Data Policy (SPD-41a) communications documents


**U.S. Geological Survey, Biogeographic Sciences Branch**, Washington, D.C., US \
*Research Ecologist* | August 2019 - August 2022 \

- Key player in establishing and facilitating cross-cutting relationships to broaden and enable partner use of agency Earth Science assets, including remotely sensed biogeographic data products, high performance computing resources, and technical expertise
- Published 3 peer-reviewed papers in top Earth Science journals, including 1 influential article outlining key priorities for synthesis in environmental research 
- Designed, developed, and published well-known open-source software to enable applications of agency's foundational data for science and applications     
- Awarded multiple performance bonuses (with SF-50 documentation) 


**University of Nebraska-Lincoln**, Lincoln, Nebraska, US \
*Graduate Research Assistant* | August 2015 - July 2019

- Developed and conducted collaborative, international research resulting in X publications and 1 book chapter
- Developed the University's first Association for Women in Science chapter, resulting in the University President's investment as an institutional member, several professional development workshops, and a sustained membership
- Delivered several scientific presentations for a diversity of audiences in local, national, and international forums


**University of Florida**, Gainesville, Florida, US \
*Graduate Research Assistant* | August 2013 - August 2015 

- Designed and conducted research resulting in X publications
- Sought and received funding to for an after school program to enable nature-based activities for at-risk-of-recidivism youth after-school program


**University of Florida**, Gainesville, Florida, US \
*Undergraduate Research Assistant* | August 2011 - August 2013 

- Did some field work, published a paper on that work
- Was trusted with key data and permitting processes for a lab PI
- Setup another PIs lab..?


**Smithsonian Institution**, Gainesville, Florida, US \
*Neighborhood Nestwatch Program* | August 2011 - August 2013 

- Led team of bird banders to conduct field work in cooperation with and in the backyards of local citizens
- Mentored and trained early career professionals on bird banding, bird identification, and data management skills
- Established program relationship with local girls youth program to conduct hands-on bird handling and viewing activities 


**Valencia Community College**, Orlando, Florida, US \
*Teaching Assistant & Tutor for Mathematics* | August 2008 - May 2010 

- Embedded in mathematics classes to encourage and facilitate learning of mathematics for community college students
- Organized and developed targeted, after-class tutoring sessions for small and large groups
- Served as Vice President of the college's student government

**Bakely's Restaurant**, Winter Haven, Florida, US \
*Front of House Manager and Server* | August 2008 - May 2010 

- Promoted to Front of House Manager within 3 months of joining as a novice restaurant server
- Hired and managed the front of house, including a team of hosts and servers, stocking, and facilities
- Managed relationships between front of house staff and kitchen personnel
- Developed and managed team schedules

**Numerous hotel jobs....**, Various , US \
** | August 2008 - May 2010 
- Can speak about varioushotel jobs, including 1 where i was promoted to a Sales position
- been working since i was 14.....



## Other Interests
- Volunteering at animal- and conservation-focused local organizations
- Competitive sand, grass, and indoor volleyball player
- Avid board, card, and video gamer

## Publications
- Will list here in reverse chronological or by topic....
<!-- ```{r, results = "asis"} -->
<!-- fa('book') -->
<!-- cat("&nbsp;&nbsp;&nbsp;2 book chapters&nbsp;&nbsp;&nbsp;") -->
<!-- fa('scroll') -->
<!-- cat("&nbsp;&nbsp;&nbsp;5 peer-reviewed journal publications&nbsp;&nbsp;&nbsp;") -->
<!-- fa('file-alt') -->
<!-- cat("&nbsp;&nbsp;&nbsp;5 conference papers&nbsp;&nbsp;&nbsp;") -->
<!-- ``` -->


Full List Available On Google Scholar: https://scholar.google.com/citations?user=rXaKU0EAAAAJ&hl=en

**Select Publications:**

<div id="refs"></div>
## Presentations
- Will list here (rev. chron. vs topical vs. invited/contributed?)