---
name: Jessica Burnett, Ph.D.
address: 5067 6th Place NE, Washington, D.C. 20017
phone: (720) 730-0974
email: jessica.burnett@nasa.gov
# website: https://github.com/trashbirdecology
geometry: left=1in,right=1in,top=1in,bottom=1in
bibliography: data/publications.bib
csl: csl/science.csl
nocite: |
  @halpern2023priorities, @burnett2021ten, @erickson2021paths, @burnett2020introduced, @burnett2019bbsassistant, @allen2019serdp, @burnett2019regime, @roberts2018early, @donovan2018social,  @lasorte2018opportunities, @chuang2018enhancing, @burnett2018thermal, @burnett2017range, @allen2016avoiding, @burnett2016songbird, @burnett2015recent
knit: (function(input, ...) {
    c(
    rmarkdown::render(
      input,
      output_format = "pdf_document",
      output_file = "burnett_resume",
      envir = globalenv()
    ),
      rmarkdown::render(
      input,
      output_format = "github_document",
      output_file = "README",
      envir = globalenv()
    ),
    rmarkdown::render(
      input,
      output_format = "word_document",
      output_file = "burnett_resume",
      envir = globalenv()
    )
    )
  })
output:
  output:
  pdf_document:
    extra_dependencies:
      fontawesome: null
      carlito: sfdefault
      fancyhdr: null
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(fontawesome)
library(rmarkdown)
```

\vspace*{-0.75in}
\thispagestyle{empty}
\centerline{\huge \bf `r metadata$name`}
\vspace{5pt}
\centerline{
\faicon{map-marker} `r metadata$address` \hspace{2 pt}
\faicon{phone} \href{tel:`r gsub("[[:space:]]", "", metadata$phone)`}{`r metadata$phone`} \hspace{2 pt}
\faicon{envelope} \href{mailto:`r metadata$email`}{`r metadata$email`} \hspace{2 pt}
}
\vspace{5pt}
\hrule

\pagestyle{fancy}
\fancyhead[L]{\textcolor[gray]{0.4}{Resume: `r metadata$name`}}
<!-- \fancyfoot[L]{\textcolor[gray]{0.4}{Document compiled on `r Sys.Date()` (\href{https://www.github.com/trashbirdecology/cv}{github.com/trashbirdecology/cv})}} -->
\pagenumbering{gobble}

```{r, results='asis', eval = knitr::is_html_output()}
cat("# ", metadata$name, "\n")
fa("map-marker")
cat("&nbsp;&nbsp;&nbsp;", metadata$address, "&nbsp;&nbsp;&nbsp;")
fa("phone")
cat("&nbsp;&nbsp;&nbsp;", metadata$phone, "&nbsp;&nbsp;&nbsp;")
fa("envelope")
cat("&nbsp;&nbsp;&nbsp;", metadata$email, "&nbsp;&nbsp;&nbsp;")
fa("home")
# cat('&nbsp;&nbsp;&nbsp;<a href="https://',
#   metadata$website,
#   '">',
#   metadata$website,
#   "</a>",
#   "&nbsp;&nbsp;&nbsp;",
#   sep = ""
# )
cat("<hr/>")
```

# Key Skills
- Over 7 years experience designing and implementing multi-year programs to answer important scientific questions, generate actionable intelligence for end user organizations, create cross-program synergies, and advance government agency missions.
- Experience in running, organizing, and serving on multiple peer review panels, including those under a dual anonymous peer review process. 
-	Passionate relationship builder whose efforts have resulting in NASA being a recognized and sought-after partner for achieving wildlife management and conservation goals in North America.
- Well-published Ph.D. life science researcher with 14 publications in top Earth science journals, 1 book chapter, 3 software programs, and over numerous government white papers and reports.
- Over a decade of experience in integrating and managing concurrent research projects with an emphasis on Earth science, especially wildlife conservation, applied geospatial science, scientific programming, and statistical modeling.
- Judicious communicator with strong interpersonal and presentation skills who has proven experience in presenting to audiences of up 500 people in person and via audio and video conferencing platforms with presentations to lay audiences, scientific communities, and decision makers alike.
- Experience in developing, evaluating, and measuring progress of multi-million dollar competitive funding solicitations. 
<!-- Program/Project Management -->
<!-- Geospatial Science and Technologies -->
<!-- Strategic Thinking -->
<!-- Earth Science Applications Research -->
<!-- Partnering -->
<!-- Financial Management -->
<!-- Technical Competence -->

# Education

**Ph.D. | Natural Resource Sciences** \
*University of Nebraska-Lincoln*, Lincoln, Nebraska | 2019 \
<!-- 15 credit hours of physical life sciences coursework, 52 credit hours of research \ -->
**M.S. | Wildlife Ecology & Conservation** \
*University of Florida*, Gainesville, Florida | 2015 \
<!-- 30 credit hours of life sciences coursework, 20 credit hours of research \ -->
**B.S. | Wildlife Ecology & Conservation**\
*University of Florida*, Gainesville, Florida  | 2013\
<!-- 74 credit hours of life sciences coursework, 5 credit hours of research\ -->
**A.A. | General Studies** \
*Valencia Community College*, Orlando, Florida | 2010 \
<!-- 42 credit hours of life sciences coursework  -->

# Professional Experience
<!-- Skills, evidence, why it matters -->
**National Aeronautics and Space Administration (NASA) Headquarters**, Washington, D.C., U.S. \
*Program Coordinator, Ecological Conservation Applications Area* | August 2022 - Present \
<!-- 40 hours per week, GS-12-2 payscale equivalent   -->

- Spearhead integration of NASA data and technologies into North American wildlife management, bridging resource gaps for conservation organizations.\ 
- Drive strategic program planning, overseeing fund solicitation, analysis, peer review panels, and proposal evaluation.\ 
- Provide expert guidance in wildlife ecology and conservation, shaping a comprehensive plan for NASA's Ecological Conservation program.\ 
- Represent NASA in high-level initiatives like the National Nature Assessment federal steering committee, the National Plan for Civil Earth Observations, and National Invasive Species Council.\ 
- Cultivate collaborative partnerships with federal, state, and non-governmental conservation organizations and landowners. Efforts resulted in key conservation agencies and organizations soliciting NASA to establish memorandum of understanding to establish long-term commitments.\  
- Advocate for the application of NASA science in wildlife and natural resource policy through representation in global and domestic science and technology working groups.\ 
- "Champion and empower students from underrepresented backgrounds, directing and supervising projects pivotal to program development, evaluation, and expansive outreach initiatives.\ 
- Serve as a technical expert on ecology and conservation issues for data calls from agencies like the White House Office of Science and Technology Policy (OSTP).\ 
- Deliver impactful messages in public forums and organize large-scale events for diverse audiences.\ 
<!-- - First-time recipient of the prestigious AAAS Science & Technology Policy fellows and the only of over 300 awardees selected to serve at NASA.\  -->
<!-- - Actively working to bring NASA data, technologies, and capacity into North American wildlife management and conservation, in a community whose organizations often lack the resources necessary to achieve conservation targets. -->
<!-- - Lead development of strategic program planning and supported program development including developing funding solicitations, program analysis, running peer review panels, and evaluating proposals. \  -->
<!-- - Serve as a wildlife ecology and conservation subject matter expert for the agency.    -->
<!-- - Lead development of a strategic plan for the Earth Science Division's Ecological Conservation program.\  -->
<!-- - Represent NASA on several executive-level initiatives including but not limited to the National Nature Assessment federal steering committee, Natural Socioeconomic Accounting Presidential Working Group, National Invasive Species Council, National Civil Earth Observations Plan writing team to ensure NASA's interests, data, and expertise are best leveraged.\  -->
<!-- - Enable land management agencies to effectively leverage NASA assets.\  -->
<!-- - Establish and manage external relationships with federal, state, and non-governmental conservation organizations and landowners.\  -->
<!-- - Develop and implement an annual outreach strategy for engaging with and synthesizing the needs of federal, state, tribal, and non-governmental end user organizations. Tactics deployed for achieving strategy include conference exhibits, sponsored events, targeted oral presentations to conservation coalitions, and developing effective communications materials.\  -->
<!-- - Represent the interests of NASA on domestic and international science and technology working groups to enable applications of NASA science for natural resource policy, management and planning.\  -->
<!-- - Supervise and mentor students from traditionally underrepresented backgrounds to conduct projects resulting in actionable intelligence for program development, evaluation, and outreach.\  -->
<!-- - Serve as technical expert for ecology and conservation issues on data calls from executive agencies such as the White House Office of Science and Technology Policy (OSTP).\ -->
<!-- , Office of Management and Budget (OMB), and Office of Personnel, and Management (OPM). \  -->
<!-- - Improve cross-organizational communications and collaborations with NASA Earth Science Data Systems and the Office of the Chief Science Data Officer, including co-sponsorship of events, writing internal guidance for NASA Open Science Data Policy (SPD-41a), and developing solicitation language to ensure policy compliance.\  -->
<!-- - As a first-time applicant, was awarded the prestigious AAAS Science & Technology Policy Fellowship and one of only two (of approximately 275) invited to support NASA Headquarters programs. \  -->
<!-- - Judiciously convey important messaging in public panels, presentations, and video conferencing platforms. Develop and deliver oral presentations to a variety of audiences ranging from scientists to federal administrators. \  -->
<!-- - Develop and organize in-person and online conferences, workshops, symposia, and special events for audiences of up to 600 people. \  -->


**U.S. Geological Survey (USGS), Biogeographic Sciences Branch**, Denver, CO\ 
*Research Ecologist and Data Scientist* | August 2019 - August 2022 \ 
<!-- 40 hours per week, GS-12-5 payscale equivalent, 2 cash awards for performance for both annual reviews conducted  \  -->

- Received cash awards for exceptional performance on all annual reviews.\ 
- Key player in establishing and facilitating cross-cutting relationships to broaden and enable partner use of agency Earth Science assets, including remotely sensed biogeographic data products, high performance computing resources, and technical expertise.\ 
- Published 3 peer-reviewed papers in top Earth Science journals, including 1 influential article outlining key priorities for synthesis in environmental research.\ 
- Designed, developed, and published well-known, open-source software to enable applications of an important USGS data asset to natural resource management and wildlife conservation activities. \ 
- Participated in several diversity initiatives focused on diversifying the scientific professional and academic communities including the Disabled in STEM, Skype a Scientist, and Letters to a Prescientist programs.\ 
- Mentored and supervised undergraduate and graduate students and young professional to achieve project tasks while setting and attaining their own professional development goals.\ 


**University of Nebraska-Lincoln (UNL)**, Lincoln, Nebraska, U.S. \ 
*Statistical and Applied Ecology Graduate Research Assistant* | August 2015 - July 2019\ 
<!-- 40 hours per week, GS-7-1 payscale equivalent  \  -->

- Created and led week-long workshop for the end users at the state of Nebraska's natural resource agency, focusing on technologies for applied statistics, data management, and applications for geospatial inference.    \ 
- Spearheaded the development of department-level and university-level activities focused on advancing awareness around and resources for women and underrepresented groups in science, including policy development, professional development and training, and university-level investments. Efforts resulted in the University President investing in the Association for Women in Science as an institutional member.\   
- Managed multiple, concurrent research projects with international and domestic collaborators, leading outreach efforts to improve applications of products for natural resource management at U.S. military bases.\ 
- Served as a mentor to several graduate and high school students while helping them set their own professional and personal development goals.\   
- Published peer reviewed articles in top natural resources and computational journals. 

**International Institute for Applied Systems Analysis**, Laxenburg, Austria \ 
*Visiting Researcher for Applied Systems Analysis* | April 2018 - August 2018 \ 
<!-- 40 hours per week, GS-7-1 equivalent  \  -->

- First-time recipient (of over 500 international applicants) of the renowned Young Scholar Summer Program fellowship, with financial support competitively awarded by the U.S. National Academy of Sciences.\  
- Designed and led collaborative research with applied mathematicians and Earth scientists, resulting in multiple international presentations, a peer-reviewed journal article, and software releases.\  


**University of Florida**, Gainesville, Florida, U.S. \ 
*Graduate Research Assistant* | August 2013 - August 2015 \ 
<!-- 40 hours per week, GS-1 payscale equivalent  \  -->

- Sought and received funding from the local police department and the University of Florida to enable nature-based activities, including new on-site trail development, at a local at-risk-of-recidivism youth program. \ 
- Designed and conducted research resulting in 3 publications and becoming a top expert on urban bird populations.\ 
- Taught and mentored undergraduate students, including developing workshops and lectures on the topics of scientific programming, invasive species, and geospatial modeling.\ 


# Personal Interests
- Enjoys competitive sports including volleyball and disc golf
- Fan of many card, board, word, and video games including spades, NYT crossword, Skyrim, and Cthulu
- Recreational baker who often shares new creations with co-workers and friends
- Volunteers as a mentor with science diversity initiatives including Disabled in STEM, Letters to a Prescientist, and Skype a Scientist
- Enjoys casually biking around town, especially when the destination is a coffee shop, library or thrift store

# Notable Awards & Achievements
- First-time applicant recipient of the prestigious AAAS Science & Technology Policy Fellowship
- First-time applicant recipient of the U.S. Geological Survey's coveted Mendenhall Postdoctoral Research Fellowship
- Received 2 cash awards for Exceptional Service during both full-fiscal years served at U.S. Geological Survey
- Recipient of over 15 competitive scholarships, fellowships, and awards totaling over $302,000
- Developed and taught over 15 professional workshops and academic courses in topics including Life Sciences, Ornithology, Ecology, and Scientific Programming
- Ran and served as a reviewer for multiple NASA peer review panels of science funding proposals 

# Publications
```{r, results = "asis"}
fa('scroll')
cat("&nbsp;&nbsp;&nbsp;14 peer-reviewed publications in Earth and life science journals&nbsp;&nbsp;&nbsp;")
fa('book')
cat("&nbsp;&nbsp;&nbsp;1 book chapter&nbsp;&nbsp;&nbsp;")
fa('file-alt')
cat("&nbsp;&nbsp;&nbsp;4 conference papers&nbsp;&nbsp;&nbsp;")
```

<!-- Full List Available On Google Scholar: https://scholar.google.com/citations?user=L0t-rQoAAAAJ&hl=en&oi=ao -->

<div id="refs">
</div>


# Select Presentations
## Invited 

1. NASA Earth Science Division: Opportunities for the Next Generation of Wildlife Professionals (presentation and panelist). *The Wildlife Society*, Louisville, KY, 2023 

1. NASA Earth Science for Forest Ecology, Conservation, and Fire Management. *Society of American Foresters*, Sacramento, CA, 2023 

1. An overview of state fish and wildlife agency use of federal geospatial data. *Association of Fish & Wildlife Agencies annual meeting*, Calgary Canada, 2023 

1. Satellite and airborne remote sensing for wildlife conservation in the West. *Western Association of Fish & Wildlife Agencies summer meeting*, Santa Fe, NM, 2023 

1. Satellite remote sensing for freshwater fisheries and aquatic sciences. *North American Wildlife and Natural Resources Conference*, St. Louis, MO, 2023 

1. Overview of NASA Earth Science Division Ecological Conservation Applications Area for USGS and U.S. Fish & Wildlife Service. *U.S. Geological Survey*, Laurel, MD, 2022 

1. Users and uses of the North American Breeding Bird Survey. Cross-organizational presentation at the *U.S. Geological Survey*, Denver, CO, 2022

1. Integrating data and information to enhance the digital efficiency of wildlife conservation and management. *North American Ornithological Conference*, Washington, D.C., 2020

1. Regime Detection Measures for the Practical Ecologist, Department of Wildlife Ecology & Conservation, University of Florida, Gainesville, FL, 2019

1. Detecting abrupt change in bird community time series using distance traveled. *Association for Women in Math Biology Symposium*, Special session "Current Challenges in Mathematical Biology ", Houston, TX , 2019

1. Decline of the Once-Ubiquitous House Sparrow in North America. *Nebraska Invasive Species Council*, Lincoln, NE , 2015     
<!-- {: reversed="reversed"}  -->

## Contributed

1. **Burnett, J.L.**. Advances in airborne and satellite remote sensing for wildlife ecology and management. *The Wildlife Society*, Oral presentation and panelist. Louisville, KY, 2023

1. **Burnett, J.L.**, N.B. Price, and A.J. Tyre. A novel method for tracking ecosystem trajectory and abrupt change in space-time: distance traveled. *International Association for Landscape Ecology*, Oral presentation. Fort Collins, CO, 2019

1. **Burnett, J.L.**, R. Crystal-Ornelas, D. Fogarty, K. Hogan, C.R. Allen, M. Bomberger Brown, D. Twidwell, and C.A. Lepczyk. Impacts of non-native birds on native wildlife in urban ecosystems: where is the evidence?  *Natural Areas Conference*, Oral presentation. Indiana, 2018

1. **Burnett, J.L.**, B. Fath, A. Rodenkova. Advances in ecological regime shift detection, *International Institute for Applied Systems Analysis*, Oral presentation. Laxenburg, Austria, 2018

1. **Burnett, J.L.**, N.B. Price, A.J. Tyre, T.J. Hefley, C.R. Allen, T. A. Eason, D.G. Angeler,and D. Twidwell. Community velocity as a regime shift detection method. *Great Plains Grassland Summit*, Poster presentation. Denver, Colorado, 2018

1. **Burnett, J.L.**, L. Wszola, N. Mirochnitchenko, E. Stuber, M. Bomberger Brown, and J.P. Carroll.  Gray partridge distribution in North America: Changing landscapes and environment for an introduced species. 33*rd* International Congress of the International Union of Game Biologists (IUGB), Oral presentation delivered by JPC, Montpellier, France, 2017

1. **Burnett, J.L.**, N.B. Price, A.J. Tyre, T.J. Hefley, C.R. Allen, T. A. Eason, D.G. Angeler, and D. Twidwell. System trajectory and Fisher information as early-warning indicators of ecological regime shifts. *Resilience 2017: Resilience Frontiers for Global Sustainability*, Poster presentation. Stockholm, Sweden, 2017

1. **Burnett, J.L.**, N.B. Price, A.J. Tyre, T.J. Hefley, C.R. Allen, T. A. Eason, D.G. Angeler,and D. Twidwell. System trajectory and Fisher information as early-warning indicators of ecological regime shifts. *Ecological Society of America*, Poster presentation. Portland, OR, 2017

1. **Burnett, J.L.**, Roberts, C.P., Allen, C.R., Angeler, D.G., Twidwell, D., and Tyre, A.J. Ecological Regime Shifts in the Central Great Plains. *Great Plains Symposium*, Oral presentation. Nebraska Innovation Campus, Lincoln, NE, 2017

1. **Burnett, J.L.**, Roberts, C.P., Allen, C.R., Angeler, D.G., Twidwell, D., and Tyre, A.J. Using Big Data to Detect Regime Shifts in Space and Time. *North American Ornithological Conference VI*, Poster presentation. Smithsonian Migratory Bird Institute, Washington, D.C., 2016

1. **Burnett, J.L.**, Moulton, M. P., Sieving, K.E., Avery, M., and Robinson, S.K. Are House Sparrow declines a byproduct of urban greening? *Southeastern Ecology and Evolution Conference*, Oral presentation. University of Georgia, Athens, GA, 2015  

1. **Burnett, J.L.**, Moulton, M. P., Sieving, K.E., Avery, M.L., and Robinson, S.K. Are House Sparrow declines a byproduct of urban greening? *American Ornithologists' Union and Cooper Ornithological Society Annual Meeting*, Poster presentation. Norman, OK, 2015  

1. **Burnett, J.L.**, Moulton, M.P., and Sieving, K.E. House sparrow: the decline of a once ubiquitous, invasive species. *Florida Chapter of The Wildlife Society Annual Conference*, Poster presentation. Safety Harbor, FL, 2014.

1. **Burnett, J.L.**, Moulton, M. P., Sieving, K.E., Avery, M.L., and Robinson, S.K. House Sparrow decline and distribution in North Central Florida. *Florida Cooperative Fish and Wildlife Research Unit annual cooperators meeting*, Poster presentation. Gainesville, FL, 2014  

1. **Burnett, J.L.** and Sieving, K.E. Detecting birds of prey using tufted titmouse distress calls. *USGS Florida Cooperative Fish and Wildlife Research Unit Committee Meeting*, Poster presentation. Gainesville, FL, 2013

1. **Burnett, J.L.** and Sieving, K.E. Do actual and perceived risks of small forest birds align? *Florida Ornithological Society Conference, Oral presentation*, St. Petersburg, FL, 2013

1. **Burnett, J.L.** and Sieving, K.E. Perceived predation risks of small forest birds. *Association of Field Ornithologists Annual Conference*, Poster presentation. Venus, FL, 2013
<!-- {: reversed="reversed"}  -->

# Conferences, Workshops & Symposia Coordination
## Symposia organization and moderation 

1. Applied Earth Observations Innovation Partnership monthly webinar series (2023-2024). *Workshop organizer*, Ann Arbor, 2024

1. Advances in airborne and satellite remote sensing for wildlife ecology and management. *Session organizer, moderator, and presenter*, The Wildlife Society annual conference, 2023

1. Bridging the gap between science and decision-making through the rapid prototyping of decision support tools. Co-organizer with D. Valle and L.S. Wszola. *Session organizer*, Ecological Society of America annual conference, 2020

1. Using the integrated modelling framework to bridge science and decision making: advances, applications, and opportunities. Co-organizer with J.A. Royle. *Session organizer, moderator, and presenter*, The Wildlife Society annual conference, 2020

1. Opportunities and Challenges in Big Data Ornithology. *Session co-organizer*, North American Ornithological Conference V, 2016

## Conference and workshop coordination   
1. Applied Earth Observations Innovation Partnership annual workshop (~200 attendees exp.). *Workshop organizer*, Ann Arbor, 2024

1. NASA Biodiversity & Ecological Conservation annual science and applications team meeting (~250 attendees, ~75 sessions). *Conference co-organizer*, Washington, D.C., 2024

1. NASA Earth Science Data and Compute workshop. *Workshop organizer and moderator* (~75 attendees), College Park, MD, 2023

1. NASA Carbon Cycle and Ecosystems Joint Science Workshop. *Conference co-organizer and moderator* (~500 attendees), College Park, MD, 2023

1. Applied Earth Observations Innovation Partnership annual workshop. *Workshop co-organizer* (~200 attendees), Salt Lake City, UT, 2023





